---
title: "R Notebook"
output: html_notebook
---

Initiating

```{r message=FALSE, warning=FALSE}
library(oro.dicom)
library(tidyverse)
library(plotly)
library(data.table)
library(htmlwidgets)
library(coreCT)
library(magick)
library(raster)
library(doParallel)
library(oro.dicom)
library(magick)
library(imager)
ref<-1000*data.frame(hmax=(4.64 +0.77),hmin=(4.64 -0.77), mmax=(3.14 + .65), mmin =(3.14- .65 ))

osis<-path.expand("E:/projects/kaggle/osic-pulmonary-fib/osic-pulmonary-fibrosis-progression")
osistrain<-path.expand("E:/projects/kaggle/osic-pulmonary-fib/osic-pulmonary-fibrosis-progression/train")
osistest<-path.expand("E:/projects/kaggle/osic-pulmonary-fib/osic-pulmonary-fibrosis-progression/test")
osisimg<-path.expand("E:/projects/kaggle/osic-pulmonary-fib/img")

#setwd(osis)

#invalids<-"ID00011637202177653955184"   #https://www.kaggle.com/rashmibanthia/corrupt-files

trd<-read.csv(file.path(osis,"train.csv"))  %>% dplyr::rename(Week=Weeks)
#subset(Patient!= invalids)
ted<-read.csv(file.path(osis,"test.csv")) %>% dplyr::rename(Week=Weeks)
invalids<-c("ID00011637202177653955184","ID00052637202186188008618", "ID00128637202219474716089","ID00132637202222178761324")

dd<-list.files(osistrain)
dd <- setdiff(dd,invalids)
pal <- colorRamp(c("black","white"))

```



*** load dicom img and convert to HU units

```{r message=FALSE, warning=FALSE}
x=dd[1]

read_x<-function(x,thr=-2000){
  path<-file.path(osistrain,x)
    s<-readDICOM(path)
    #img<-s$img[[index]] 
    
    ct.slope <- unique(extractHeader(s$hdr, "RescaleSlope"))
    ct.int   <- unique(extractHeader(s$hdr, "RescaleIntercept")) 
    Ct.n<- extractHeader(s$hdr, "InstanceNumber")
    s1 <- lapply(s$img, function(x) x*ct.slope + ct.int) 
   # ff<-function(x){x [ x < -2000 ]<- NA;return(x)}
    # trim background
    s2<-  lapply(s1,function(y){y[y< thr]<-F;return(y)})
    #reorder:
    fo<-function(i){
      index<-which(Ct.n ==i)
      return(s2[[index]])
    }
    so<-lapply(1:length(s2),fo)
    return(so)
}
so<-read_x(x,thr=-2000)
    
```
**imager

```{r}

xx<-function(x){
  out<-as.cimg(x) %>% imrotate(angle = -90)
  return(out)
}
l.im<- lapply(so,xx)

img<-as.imlist(l.im)

#layout(matrix(1:30,ncol = 3,byrow = T))
par(mar = c(0,0,0,0),mai=c(0,0,0,0))

plot(img,axes = F)

```


```{r}
img<-so[[13]]



im<-as.cimg( img ) %>% imrotate(angle=-90)
plot(im)
```

*** more imager processing


```{r}
px<-(im < - 600 & im > -860 )

plot(px)
```




```{r}
plot(im)
highlight(px)


```
```{r}
plot(im)
px.flood(im,78,296,sigma=.001) %>% highlight

```







```{r}


pal <- colorRamp(c("black","white"))

fig <- plot_ly(z = ~ so[[7]], colors = pal) %>%
add_surface(
  contours = list(
    z = list(
      show=TRUE,
      usecolormap=TRUE,
      highlightcolor="#ff0000",
      project=list(z=TRUE)
    )
  )
)
fig <- fig %>% layout(
  scene = list(
    camera=list(
      eye = list(x=1.87, y=0.88, z=-0.64)
    )
  )
)

fig

```

** new threshould to focus on lungs

```{r}
sfail<-read_x(x,-600)
pal <- colorRamp(c("black","white"))

fig <- plot_ly(z = ~ sfail[[7]], colors = pal) %>%
add_surface(
  contours = list(
    z = list(
      show=TRUE,
      usecolormap=TRUE,
      highlightcolor="#ff0000",
      project=list(z=TRUE)
    )
  )
)
fig <- fig %>% layout(
  scene = list(
    camera=list(
      eye = list(x=1.87, y=0.88, z=-0.64)
    )
  )
)

fig
```

It has cut most of the lungs...that is below -800



 **** lets start lung segmentation
linear model:

```{r}
d <- as.data.frame(im)
##Subsamble, fit a linear model
m <- sample_n(d,1e4) %>% lm(value ~ x*y,data=.) 
##Correct by removing the trend
im.c <- im-predict(m,d)
out <- threshold(im.c)
plot(out)

```



```{r}
 out<-threshold(im,"auto")
out <- clean(out,10) %>%  imager::fill(7)
plot(im)
highlight(out)


```

```{r}
imo<-im
imo[ out]<- NA
plot(imo)
```

```{r}
 fig1<-plot_ly(
            z = as.matrix( so[[7]] %>% imrotate(90)),
            #colorscale = list(c(0,0.5,1),c("blue", "white", "red")),
            colors=pal,
            type = "heatmapgl"
            ) 


 fig2<-plot_ly(
            z = as.matrix(so[[13]]%>% imrotate(90)),
            #colorscale = list(c(0,0.5,1),c("blue", "white", "red")),
            colors=pal,
            type = "heatmapgl"
            ) 
 
 fig3<-plot_ly(
            z = as.matrix(so[[18]]%>% imrotate(90)),
            #colorscale = list(c(0,0.5,1),c("blue", "white", "red")),
            colors=pal,
            type = "heatmapgl"
            ) 
fig1
fig2
fig3

```



```{r}
layout(t(1:2))
out<-threshold(im)
a<-kmeans(out,2)
colors<- as.cimg(a$centers[a$cluster,])
plot(out)
px<-colors==1
highlight(px * out)

plot(out)
px<-colors==2
highlight(px * out)





```

```{r}
plot(out)
px<-colors==2
highlight(px * out)
```



```{r}
#im<-as.cimg(so[[7]]) %>% imrotate(-90)


detect.edges <- function(im,sigma=2)
    {
        isoblur(im,sigma) %>% imgradient("xy") %>% enorm 
    }

edges <- detect.edges(im,2) %>% sqrt 
plot(edges)
pmap <- 1/(1+edges) #Priority inv. proportional to gradient magnitude
plot(pmap,main="Priority map") #Nice metal plate effect! 


```
Will be a little harder to find a priority map that targets whole lung, that what we want. 
```{r}
seeds <- imfill(dim=dim(pmap)) #Empty image
seeds[170,233,1,1] <- 1 #Background pixel 
seeds[36,255,1,1] <- 2 #Foreground pixel

wt1 <- watershed(seeds,pmap)
plot(wt1,main="Watershed segmentation")





```
the other lung

```{r}
seeds <- imfill(dim=dim(pmap)) #Empty image
seeds[355,247,1,1] <- 1 #Background pixel 
seeds[56,252,1,1] <- 2 #Foreground pixel

wt2 <- watershed(seeds,pmap)
plot(wt2,main="Watershed segmentation")


```
now, both

```{r}

wt <- wt1 + wt2

plot(wt)


```

```{r}
wt[wt==3]<-T
wt[wt==4]<-NA
lungs<-wt * im
plot(lungs)


```




Lets automate the choose for those pixels to watershed

Lungs point

```{r}
ylim<-floor(0.4 * 512):floor(0.6 *512)
xlim1<-floor(0.2 * 512):floor(0.3 * 512); xlim2<-floor( 0.6 *512) :floor( 0.8 * 512)
xlim<-c(xlim1,xlim2)
ima<-im[xlim,ylim,1,1]
out<-matrix(rep(F,512^2 ),ncol=512)


###lung d
out[xlim1,ylim]<-T
out<-as.cimg(out)
plot(im)
highlight(out)
pmatrix<-out * im
pr<-which(pmatrix == min(pmatrix), arr.ind = TRUE)[1,]

####lung e
out[xlim2,ylim]<-T
out<-as.cimg(out)
plot(im)
highlight(out)
pmatrix<-out * im
pl<-which(pmatrix == min(pmatrix), arr.ind = TRUE)[1,]


```
Everywere


```{r}

ylim<-floor(0.7 * 512):floor(0.75 *512)
xlim<-c(floor(0.4 * 512):floor(0.6 * 512))
ima<-im[xlim,ylim,1,1]
out<-matrix(rep(F,512^2 ),ncol=512)
out[xlim,ylim]<-T
out<-as.cimg(out)
plot(im)
highlight(out)
pmatrix<-out * im
p2<-which(pmatrix == min(pmatrix), arr.ind = TRUE)[1,]

```
Everything together

```{r}
detect.edges <- function(im,sigma=1)
    {
        isoblur(im,sigma) %>% imgradient("xy") %>% enorm %>% imsplit("c") %>% add
    }

edges <- detect.edges(im,2) %>% sqrt 
pmap <- 1/(1+edges) #Priority inv. proportional to gradient magnitude
seeds <- imfill(dim=dim(pmap)) #Empty image
seeds[pr[1],pr[2],pr[3],pr[4]] <- 1 #Background pixel 
seeds[p2[1],p2[2],p2[3],p2[4]] <- 2 #Foreground pixel

wt1 <- watershed(seeds,pmap)
plot(wt1,main="Watershed segmentation")


###
seeds[pl[1],pl[2],pl[3],pl[4]] <- 1 #Background pixel 
seeds[p2[1],p2[2],p2[3],p2[4]] <- 2 #Foreground pixel

wt2 <- watershed(seeds,pmap)
plot(wt2,main="Watershed segmentation")




```
finally, a function

```{r}
masks<-function(im1){

  im<- im1 %>%
    as.cimg %>%
    imrotate(angle = -90)

  
  ylim<-floor(0.4 * 512):floor(0.6 *512)
  xlim1<-floor(0.2 * 512):floor(0.3 * 512); xlim2<-floor( 0.6 *512) :floor( 0.8 * 512)
  xlim<-c(xlim1,xlim2)
  ima<-im[xlim,ylim,1,1]
  out<-matrix(rep(F,512^2 ),ncol=512)
  ###lung d
  out[xlim1,ylim]<-T
  out<-as.cimg(out)
  #plot(im)
  #highlight(out)
  pmatrix<-out * im
  pr<-which(pmatrix == min(pmatrix), arr.ind = TRUE)[1,]
  
  ####lung e
  out[xlim2,ylim]<-T
  out<-as.cimg(out)
  #plot(im)
  #highlight(out)
  pmatrix<-out * im
  pl<-which(pmatrix == min(pmatrix), arr.ind = TRUE)[1,]

  
  
  
  
  ylim<-floor(0.7 * 512):floor(0.75 *512)
  xlim<-c(floor(0.4 * 512):floor(0.6 * 512))
  ima<-im[xlim,ylim,1,1]
  out<-matrix(rep(F,512^2 ),ncol=512)
  out[xlim,ylim]<-T
  out<-as.cimg(out)
  #plot(im)
  #highlight(out)
  pmatrix<-out * im
  p2<-which(pmatrix == min(pmatrix), arr.ind = TRUE)[1,]



  detect.edges <- function(im,sigma=1)
      {
          isoblur(im,sigma) %>% imgradient("xy") %>% enorm %>% imsplit("c") %>% add
      }
  
  edges <- detect.edges(im,2) %>% sqrt 
  pmap <- 1/(1+edges) #Priority inv. proportional to gradient magnitude
  seeds <- imfill(dim=dim(pmap)) #Empty image
  seeds[pr[1],pr[2],pr[3],pr[4]] <- 1 #Background pixel 
  seeds[p2[1],p2[2],p2[3],p2[4]] <- 2 #Foreground pixel
  
  wt1 <- watershed(seeds,pmap)
  #plot(wt1,main="Watershed segmentation")
  
  
  ###
  seeds[pl[1],pl[2],pl[3],pl[4]] <- 1 #Background pixel 
  seeds[p2[1],p2[2],p2[3],p2[4]] <- 2 #Foreground pixel
  
  wt2 <- watershed(seeds,pmap)
  #plot(wt2,main="Watershed segmentation")
    wt1[wt1==1]<-T;wt1[wt1!=1]<-F
        wt2[wt2==1]<-T;wt2[wt2!=1]<-F
   wt<- wt1 | wt2

  
  # wt<-wt1+wt2
  # wt[wt==3]<-T
  # wt[wt==4]<-NA
  lungs<-wt * im
  return(lungs)
  #plot(lungs)

}


```

loop over all imgs from this patient

```{r}
loopd<-function(so){
 a<- so%>%
    map(masks) %>%
   map(plot)
}


```
coreCT

HU units considered

```{r}
a<-coreHist("core_426")
a$split
```

CoreCT
```{r}
et<-function(tag){
  a1<-extractHeader(s$hdr,tag ,numeric=FALSE) %>%
    as.list %>%
    str_split(pattern =" ")
  a2<-lapply(a1,as.numeric)
  return(a2)
}
st<-extractHeader(a$hdr,"SliceThickness")
ps<-et("PixelSpacing")
#materials <- convert(HU_426, pixelA = 0.0596)

```


