---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

T
```{r message=FALSE}
library(oro.dicom)
library(tidyverse)
library(plotly)
library(data.table)
library(htmlwidgets)
library(coreCT)
library(magick)
library(raster)
library(doParallel)
library(oro.dicom)
library(magick)
library(imager)
ref<-1000*data.frame(hmax=(4.64 +0.77),hmin=(4.64 -0.77), mmax=(3.14 + .65), mmin =(3.14- .65 ))

osis<-path.expand("E:/projects/kaggle/osic-pulmonary-fib/osic-pulmonary-fibrosis-progression")
osistrain<-path.expand("E:/projects/kaggle/osic-pulmonary-fib/osic-pulmonary-fibrosis-progression/train")
osistest<-path.expand("E:/projects/kaggle/osic-pulmonary-fib/osic-pulmonary-fibrosis-progression/test")
osisimg<-path.expand("E:/projects/kaggle/osic-pulmonary-fib/img")

#setwd(osis)

#invalids<-"ID00011637202177653955184"   #https://www.kaggle.com/rashmibanthia/corrupt-files

trd<-read.csv(file.path(osis,"train.csv"))  %>% dplyr::rename(Week=Weeks)
#subset(Patient!= invalids)
ted<-read.csv(file.path(osis,"test.csv")) %>% dplyr::rename(Week=Weeks)
invalids<-c("ID00011637202177653955184","ID00052637202186188008618", "ID00128637202219474716089","ID00132637202222178761324")

dd<-list.files(osistrain)
dd <- setdiff(dd,invalids)
x=dd[1]





```

```{r message=FALSE, warning=FALSE}
read_x<-function(x,thr){
  path<-file.path(osistrain,x)
    s<-readDICOM(path)
    #img<-s$img[[index]] 
    
    ct.slope <- unique(extractHeader(s$hdr, "RescaleSlope"))
    ct.int   <- unique(extractHeader(s$hdr, "RescaleIntercept")) 
    Ct.n<- extractHeader(s$hdr, "InstanceNumber")
    ss <- lapply(s$img, function(x) x*ct.slope + ct.int) 
   # ff<-function(x){x [ x < -2000 ]<- NA;return(x)}
    # trim background
    ss<-  lapply(ss,function(x){x[x< thr]<-F;return(x)})
    #reorder:
    fo<-function(i){
      index<-which(Ct.n ==i)
      return(ss[[index]])
    }
    so<-lapply(1:length(ss),fo)
   # convert to imager and rotate. return(so)
    conv<-function(x){
      out<- x %>% as.cimg %>% imrotate(angle = -90)
       return(out)
    }
    out<-lapply(so,conv)
}

so<-read_x(x,-2000)
liply(so[17:22],threshold,"x") %>% plot# apply func and append

im<-so[[18]]

```




How many files are there by patient?
```{r message=FALSE, warning=FALSE}
nf<-function(x){
  p<-file.path(osistrain,x)
  return(length(list.files(p)))
}
nfs<-sapply(dd,nf)
nfs
summary(nfs)
```

I really need an algo to select imgs

```{r}
d <- as.data.frame(im)
##Subsamble, fit a linear model
#m <- sample_n(d,1e4) %>% lm(value ~ x*y,data=.) 
m <- sample_n(d,1e4) %>% lm(value ~ x*y,data=.) 

##Correct by removing the trend
im.c <- im-predict(m,d)
out <- threshold(im.c)
plot(out)
b<- !out * im

```
now, with all img


```{r}
d <- as.data.frame(im)

m <- d %>% lm(value ~ x*y,data=.) 

##Correct by removing the trend
im.c <- im-predict(m,d)
out <- threshold(im.c) %>% shrink(0)

layout(t(1:2))
plot(out)
plot(im)
```
```{r}

plotq<-function(im){
  px <- (isoblur(im,4)  > .5 ) %>% clean(5) %>% imager::fill(7)
  
  
#    out<-threshold(im,"auto")
# out <- clean(out,5) %>% imager::fill(7)
  
  plot(im)
  highlight(px)
  #Grow by 5 pixels
  # grow(px,px.circle(10)) %>% highlight(col="green")
  #Shrink by 5 pixels
  # shrink(px,5) %>% highlight(col="blue")
  
  #Compute bounding box
  bbox(px) %>% highlight(col="yellow")
}
  plotq(im)
  
```
```{r}
out<-threshold(im,"auto")
out <- clean(out,10) %>% imager::fill(7) %>% shrink(10)
layout(t(1:2))
plot(im)
highlight(out)
plot(out)


```
```{r}

layout(t(1:2))
out<- 1- threshold(im,"auto")
out %>% plot
plot(out %>% clean(2))

m<-1- (out %>% clean(2))
plot(im)
plot(m)



out <- clean(m,20) %>% shrink(2)
layout(t(1:2))
plot(im)
highlight(out)
plot(out)



plot((!out) * im) #== plot(im * (out==0))
```



# Liked this division
```{r}
  pp<-function(im){

  par(mar = c(0,0,0,0),ann=F)
  layout(t(1:5))
  out<- 1- threshold(im,"auto")
  #out %>% plot
  #plot(out %>% clean(2))
  
  m<-1- (out %>% clean(2))
  plot(im)
  plot(m)
  
  
  
  out <- clean(m,20) %>% shrink(2)
  plot(im)
  highlight(out)
  plot(out)
  plot((!out) * im) #== plot(im * (out==0))<-function(im){
    
  
  
}

```

```{r}
walk(so,pp)
```


```{r}


pp<-function(x){
  img<-so[[x]]
  plot(threshold(img),axes=F)
  plotq(img)
}
par(mar = c(0,0,0,0))
#par(mai = c(0,0,0,0))
layout(matrix(1:24,ncol=6, byrow=F))
walk(1:12,pp)


```

```{r}
par(mar = c(0,0,0,0))
#par(mai = c(0,0,0,0))
layout(matrix(1:24,ncol=6, byrow=T))
walk(1:12,pp)

```

```{r message=FALSE, warning=FALSE}
par(mar = c(0,0,0,0))
#par(mai = c(0,0,0,0))
layout(matrix(1:24,ncol=6, byrow=T))
walk(13:24,pp)

```
```{r}
# pal <- colorRamp(c("black","white"))
# 
#  a<-data.table(so=so[5:10],i=1:length(so[5:10]))
#  fig<-a %>% plot_ly(
#             z = ~ so,
#             #colorscale = list(c(0,0.5,1),c("blue", "white", "red")),
#             colors=pal,
#             type = "heatmapgl",
#             frame = ~ i
#             ) %>%
#      animation_slider()
# 


```

```{r}

pal <- colorRamp(c("black","white"))

 plot_ly(
            z = ~ as.matrix(so[[18]] %>% imrotate(90)),
            #colorscale = list(c(0,0.5,1),c("blue", "white", "red")),
            colors=pal,
            type = "heatmapgl"
            #frame = ~ i
            ) 
```


Now, i can set the bondary of the bones and elminate most of artefacts around

```{r}
# 
# ima <- as.cimg(function(x,y) sin(x/5)+cos(x/4)*sin(y/2),128,128)
# ff <- FFT(ima)
# plot(ff$real,main="Real part of the transform")
# 
# 
# 
# ff<-FFT(im)
# sqrt(ff$real^2+ff$imag^2) %>% plot(main="Power spectrum")
# 
# 
# plot(im)
# px <- (isoblur(im,4)  < .1 )
# highlight(px)
# 
# 
px <- (isoblur(im,4)  > .5 )
sp <- split_connected(px) #returns an imlist
plot(sp[1:4])
boundary(px) %>% plot



plot(im)
highlight(px)
#Grow by 5 pixels
grow(px,5) %>% highlight(col="green")
#Shrink by 5 pixels
shrink(px,5) %>% highlight(col="blue")

#Compute bounding box
bbox(px) %>% highlight(col="yellow")


box<-bbox(px)
ima<-im
ima[!box]<-F
th<-threshold(ima)%>% clean(7) %>% imager::fill(7)
plot(th)
#ima[box]<-NA
#plot(ima)
select_box<-function(x){
  px <- (isoblur(x,4)  > .5 ) %>% bbox
  x[!px]<-0
  return(x)
}


```
```{r}
skeleton<-im * px
pxn <- (isoblur(im,4)  > .5 )

nskeleton <- im * (!px)

fig1<-plot_ly(
            z = t(as.matrix(skeleton)),
            colorscale = list(c(0,0.5,1),c("blue", "white", "red")),
            #colors="Greys",
            type = "heatmapgl"
            )
fig2<-plot_ly(
            z = t(as.matrix(nskeleton)),
            colorscale = list(c(0,0.5,1),c("blue", "white", "red")),
            #colors="Greys",
            type = "heatmapgl"
            )
layout(t(1:2))
fig1
fig2
a<-threshold(nskeleton)
plot(a)
```


```{r}
a<-imgradient(nskeleton)
layout(t(1:2))
plot(a$x);plot(a$y)

```
```{r}
layout(t(1:2))
 plot(threshold(a$x))
 plot(threshold(a$y))
```

Now, trying to applyu Fourier Transform
first, a very improvment over https://dahtah.github.io/imager/imager.html

```{r}
ima <- as.cimg(function(x,y) sin(x/5)+cos(x/4)*sin(y/2),128,128)
ff <- FFT(ima)
ffp <- sqrt(ff$real^2+ff$imag^2) 
s<-scale(as.matrix(ffp)) %>% as.cimg
plot(s)

```


```{r}
ff <- FFT(im)
ffp <- sqrt(ff$real^2+ff$imag^2) 
summary(ffp)
s<-scale(as.matrix(ffp)) %>% as.cimg
summary(s)
plot(s)

```
# filter low band

```{r}
ff <- FFT(im)
layout(t(1:2))
plot(ff$real,main="Real")
plot(ff$imag,main="Im")
ffp <- sqrt(ff$real^2+ff$imag^2) 
summary(ffp)
s<-scale(as.matrix(ffp)) %>% as.cimg
ff$real[s< 1]<-F   #as.cimg (get.locations(s,function(x)x < 0))
ff$imag[s< 1]<-F

plot(ff$real,main="Real after filter")
plot(ff$imag,main="Im after filter")
fim<-FFT(ff$real,ff$imag,inverse = T)
layout(t(1:3))
plot(im)
plot(fim$real,main="FFT filtered real")
plot(fim$imag,main="FFT filtered imag")

par(mar = c(0,0,0,0))
layout(t(1:2))
plot(threshold(im))
plot(threshold(fim$real),main= "FFT real")


```
Now, high frequencies

```{r}
ff <- FFT(im)
layout(t(1:2))
plot(ff$real,main="Real")
plot(ff$imag,main="Im")
ffp <- sqrt(ff$real^2+ff$imag^2) 
summary(ffp)
s<-scale(as.matrix(ffp)) %>% as.cimg
ff$real[s> 15]<-F   #as.cimg (get.locations(s,function(x)x < 0))
ff$imag[s> 15]<-F

plot(ff$real,main="Real after filter")
plot(ff$imag,main="Im after filter")
fim<-FFT(ff$real,ff$imag,inverse = T)
layout(t(1:3))
plot(im)
plot(fim$real,main="FFT filtered real")
plot(fim$imag,main="FFT filtered imag")

par(mar = c(0,0,0,0))
layout(t(1:2))
plot(threshold(im))
plot(threshold(fim$real),main= "FFT real")
```

very low difference
lets make more filters 

```{r}
layout(t(1:2))
 fim$real %>% threshold %>% clean(15) %>% imager::fill(5 ) %>% plot
 im %>% plot

 
 
```
```{r}
layout(t(1:2))
 im %>% threshold %>% clean(20) %>% imager::fill(5 ) %>% plot
 im %>% plot

 


```
This is a lot worse... lets filter in a nicer way
```{r}
filterbones<-function(im){
  px <- (isoblur(im,4)  > .5 ) %>% clean(5) %>% grow(4) %>% imager::fill(15)
  # plot(im)
  # highlight(px)
  return(px)
}
filterbones(im)
```


```{r}


ffts<-function(im,lim,cl,fi ){
  bones<-filterbones(im)
  ff <- FFT(im)
  ffp <- sqrt(ff$real^2+ff$imag^2) 
  s<-scale(as.matrix(ffp)) %>% as.cimg
  ff$real[s< lim]<-F   #as.cimg (get.locations(s,function(x)x < 0))
  ff$imag[s< lim]<-F
  fim<-FFT(ff$real,ff$imag,inverse = T)

  par(mar = c(0,0,0,0))
   layout(t(1:2))
   nobones<-fim$real * (!bones)
   nobones %>% threshold %>% clean(cl) %>% imager::fill(fi ) %>% plot
   nobones %>% plot

}
ffts(im,1,20,10)

```





Lets denoise and etc:
```{r}
ima<-select_box(im)
gr <- imgradient(ima,"xy")
plot(gr,layout="row")

```

```{r}
mag <- with(gr,sqrt(x^2+y^2))
plot(mag)


```
The Canny edge detector is essentially a cleaned-up version of the above picture.

The gradient angle determines the local orientation of image edges:

```{r}


ang <- with(gr,atan2(y,x))
plot(ang)
```
```{r}
cs <- scales::gradient_n_pal(c("red","darkblue","lightblue","red"),c(-pi,-pi/2,pi/2,pi))
par(mar = c(0,0,0,0))
layout(t(1:2))
plot(ang,colourscale=cs,rescale=FALSE)
threshold(mag) %>% plot

```
A gradient( parentesis )

```{r}
gradfield <- function(im,subs=4)
    {
        gr <- imgradient(im,"xy")
        names(gr) <- c("dx","dy")
        dgr <- as.data.frame(gr) %>% tidyr::spread(im,value)
        dgr <- dplyr::filter(dgr,(x %% subs) ==0,(y %% subs) == 0)
        dgr <- dplyr::mutate(dgr,mag=sqrt(dx^2+dy^2), #Gradient magnitude
                                 dxs=dx/mag,dys=dy/mag,#Scale every vector to unit size
                                 xend = x + 2*dxs,yend = y +2*dys) 
        p <- as.data.frame(im) %>% ggplot(aes(x,y))+geom_raster(aes(fill=value))
        p <- p+geom_segment(data=dgr,aes(xend=xend,yend=yend,alpha=mag),arrow = arrow(length = unit(0.01, "npc")),col="red")
        p+scale_y_reverse()+scale_fill_continuous(low="black",high="white")
    }

gradfield(ima,6)

```
more denoising



```{r}
#Going along the (normalised) gradient
#Xc(im) is an image containing the x coordinates of the image
nX <- Xc(im) + gr$x/mag 
nY <- Yc(im) + gr$y/mag
#nX and nY are not integer values, so we can't use them directly as indices.
#We can use interpolation, though:
val.fwd <- interp(mag,data.frame(x=as.vector(nX),y=as.vector(nY)))
nX <- Xc(im) - gr$x/mag 
nY <- Yc(im) - gr$y/mag
val.bwd <- interp(mag,data.frame(x=as.vector(nX),y=as.vector(nY)))

throw <- (mag < val.bwd) | (mag < val.fwd)
mag[throw] <- 0
plot(mag)


```

```{r}
#strong threshold
t2 <- quantile(mag,.96)
#weak threshold 
t1 <- quantile(mag,.90)
layout(t(1:2))

strong <- mag>t2
plot(strong,main="Initial set of strong edges")
weak <- mag %inr% c(t1,t2)
plot(weak,main="Initial set of weak edges")
```
histerese rescue

```{r}
hyst.loop <- function(strong,weak)
    {
        #We make the queue a list so that it can grow or shrink relatively fast
        queue <- which(strong==1) %>% as.list
        max.x <- width(strong)
        max.y <- height(strong)
        while (length(queue)>0)
            {
                ind <- queue[[1]]
                #get (x,y) coordinates of the current point
                cc <- coord.index(strong,ind)
                #explore the neighbourhood
                for (nx in (cc$x+c(-1,0,1)))
                {
                    for (ny in (cc$y+c(-1,0,1)))
                    {
                        #we have to mind boundary conditions
                        if (nx > 0 && nx <= max.x && ny > 0 && ny <= max.y)
                        {
                            if (at(weak,nx,ny)==TRUE)
                            {
                                at(weak,nx,ny) <- FALSE
                                at(strong,nx,ny) <- TRUE
                                queue[[length(queue)+1]] <- index.coord(strong,data.frame(x=nx,y=ny))
                            }
                        }
                    }
                }
                queue[[1]] <- NULL
            }
        strong
    }

canny <- hyst.loop(strong,weak)
plot(canny,main="Edges after hystereris")


```
# morphological dilation

```{r}

px <- imnoise(100,100) > 1
layout(t(1:2))
plot(px,"Original")
plot(grow(px,3),"Dilated Set")


```
```{r}
overlap <- grow(strong,3) & weak 
strong.new <- strong | overlap
plot(strong.new,main="New set of strong edges")
delta <- sum(strong.new)-sum(strong)
delta

```


didnt worked


but now, with flood fill

```{r}
pxs <- split_connected(strong,high_connectivity=TRUE)
length(pxs)
plot(strong)
library(purrr)
map_df(pxs,~ where(.)[1,]) %$% points(x,y,col="red")


```
For the bucket fill trick to work we need to be able to spread the value of strong pixels to their weak neighbour (but not elsewhere). We assign different values to strong and weak pixels:


```{r}

v <- as.cimg(strong)
v[weak==1] <- .9 #Strong pixels have value 1, weak .9, and the rest are 0.
```
Finally we need to go through the list of seed pixels, and apply bucket fill every time. We could write a loop, but to keep with the functional style we have used so far, we’ll cast this operation as a fold, using reduce from the purrr package. reduce takes a function of two arguments (an accumulator and an item), and reduces a list to a single item by accumulating. It’s best illustrated by example:

```{r}
library(purrr)
add <- function(l) reduce(l,function(acc,item) acc+item,.init=0)
add(1:3) #equals sum(1:3)

```

```{r}
parrots<-im
plot(parrots)
points(180,229,col="red")
px.flood(parrots,180,229,sigma=.1) %>% highlight
#Higher tolerance
px.flood(parrots,180,229,sigma=.14) %>% highlight(col="darkred")
#Different initial point
px.flood(parrots,180,229,sigma=.1) %>% highlight(col="blue")
```
lets print some 3d part
```{r}
toSide<-function(im,ll=128){
   ln<- im %>% as.matrix
   return(ln[,ll])
}
#toSide(so[[1]])
toSides<-function(so,ll=128){
  la<-sapply(so,toSide,ll=ll) %>% t %>% 
  as.cimg %>% resize(size_x = 512, size_y = 512) %>% imrotate(90)
  return(la)
}
v<-seq(50,450,50)
lsides<-lapply(v,FUN = toSides,so=so)
imappend(lsides,"x") %>% plot


```

